---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wetried

Names: Chi Qiu, Meaghan Brennan, and Emma Gardecki

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/wetried2)](https://CRAN.R-project.org/package=wetried2)

<!-- badges: end -->

## Purpose

The purpose of `wetried` package is to be a Smith College basketball version of the nbastatr package, but in a simpler form. It uses the season totals as provided on the Smith Athletics website and will all for users to calculate advanced stats on their own, such as TS%. With it, you can see the Smith College basketball team's stats and calculate various advanced stats and any important numbers that are useful for evaluating the performance of a basketball game.

## Target Audience

Users who may be interested in this package would be anyone interested in Smith College's basketball team, as well as anyone interested in sports analytics and specifically basketball analytics. This package also provides a useful way for coaches to learn more about the team and how to improve it.

## Installation

You can install IPEDS from [CRAN](https://cran.r-project.org/) with:

```{r}
#install.packages("wetried2")
```

You can install the development version of wetried2 from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("chiqiu23/wetried")
```

## Load

```{r load}
library(wetried2) 
```

## Available Tables

-   `smith_wbb_data`: dataset of Smith College Women Basketball Games for 2010-2022 season

## Example: 2010-2022 Cumulative Statistics for Smith College Women Basketball Game

```{r wbb data}
head(smith_wbb_data)
```

### Data Visualization

```{r pressure, echo = FALSE}
#smith_wbb_example <- smith_wbb_data |> 
  #filter(number == "10"| number == "22", season == "2021-22")
#view(smith_wbb_example) 

#ggplot(smith_wbb_example, mapping = aes(x = player, fill = fgm))+
  #geom_bar()
```

### Efficiency Calculation

## Project Proposals for Phase III

## Contributors

-   [Chi Qiu](https://github.com/chiqiu23)

-   [Meaghan Brennan](https://github.com/teenyss)

-   [Emma Gardecki](https://github.com/emmagardecki)
