---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wetried2

Names: Chi Qiu, Meaghan Brennan, and Emma Gardecki

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg){alt="Lifecycle: experimental"}](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/wetried2){alt="CRAN status"}](https://CRAN.R-project.org/package=wetried2) [![R-CMD-check](https://github.com/chiqiu23/wetried/actions/workflows/R-CMD-check.yaml/badge.svg){alt="R-CMD-check"}](https://github.com/chiqiu23/wetried/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

## Purpose

The purpose of `wetried2` package is to be a Smith College basketball version of the nbastatr package, but in a simpler form. It uses the season totals as provided on the Smith Athletics website and will all for users to calculate advanced stats on their own, such as TS%, and provide visualizations for analysis.

## Target Audience

Users who may be interested in this package would be anyone interested in Smith College's basketball team, as well as anyone interested in sports analytics and specifically basketball analytics. This package also provides a useful way for coaches to learn more about the team and how to improve it.

## Installation

You can install the development version of `wetried2` from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("chiqiu23/wetried")
```

## Load

```{r load}
library(wetried2) 
```

## Available Datasets

-   `smith_wbb_data`: dataset of Smith College Women Basketball Games for 2010-2022 season (with exception for the 2019-2020 season that was disrupted by the Covid-19 Pandemic)
-   `smith_oppwbb_data`: dataset of opponents of Smith College Women Basketball Games for 2010-2022 (with exception for the 2019-2020 season that was disrupted by the Covid-19 Pandemic)

## Available functions

-   `TS_percentage()`: calculate TS% or True Shooting Percentage from the Smith WBB dataset
-   `perform_players()`: compare field goals attempted for two selected players across one season
-   `ast_turnover_ratio()`: calculate the assist to turnover ratio of a player from the Smith WBB dataset
-   `offensive_rating()`: calculate the offensive rating of a player from the Smith WBB dataset and Opponents' of Smith WBB dataset

## Example: 2010-2022 Cumulative Statistics for Smith College Women Basketball Game

```{r wbb data}
head(smith_wbb_data)
```

### Calculate True Shooting Percentage

```{r}
TS_percentage(input_player = "Bondi, Lauren", input_season = "2018-19")
```

### Calculate Assist to Turnover Ratio Calculation

```{r}
ast_turnover_ratio(input_player = "Pickunka, Katelyn", input_season = "2021-22")
```

### Compare Field Goals Attempted of Two Players

```{r}
perform_players(player_num1 = 10, player_num2 = 22, input_season = "2021-22")
```

## Example: 2010-2022 Cumulative Statistics for Opponents of Smith College Women Basketball Game

```{r oppwbb data}
head(smith_oppwbb_data)
```

### Calculate Offensive Rating of the Player

```{r}
offensive_rating(input_player = "Bondi, Lauren", input_season = "2018-19")
```

## Contributors

-   [Chi Qiu](https://github.com/chiqiu23)

-   [Meaghan Brennan](https://github.com/teenyss)

-   [Emma Gardecki](https://github.com/emmagardecki)
