---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wetried

Names: Chi Qiu, Meaghan Brennan, and Emma Gardecki
 
<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/wetried2)](https://CRAN.R-project.org/package=wetried2)

<!-- badges: end -->

## Purpose

The goal of `wetried` package is to be a Smith College version of the nbastatr package -- with it, you can see the Smith College basketball team's stats and calculate various advanced stats and any important numbers that are useful for evaluating the performance of a basketball game.

## Target Audience

Anyone who is interested in analyzing the performance of Smith College basketball games. This package also provides a useful way for coaches to learn more about the team and how to improve it.

## Installation

You can install IPEDS from [CRAN](https://cran.r-project.org/) with: 

```{r}
#install.packages("wetried2")
```

You can install the development version of wetried2 from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("chiqiu23/wetried")
```

## Load

```{r load}
library(wetried2) 
```

## Available Tables

-   `smith_wbb_data`: dataset of Smith College Women Basketball Games for 2010-2022 season

## Example: 2010-2022 Cumulative Statistics for Smith College Women Basketball Game 

```{r wbb data}
library(readr)
smith_wbb_data <- read_csv("smith_wbb_data.csv")
head(smith_wbb_data)
```

### Data Visualization 

```{r pressure, echo = FALSE}
#smith_wbb_example <- smith_wbb_data |> 
  #filter(number == "10"| number == "22", season == "2021-22")
#view(smith_wbb_example) 

#ggplot(smith_wbb_example, mapping = aes(x = player, fill = fgm))+
  #geom_bar()
```

### Functionality

## Contributors

-   [Chi Qiu](https://github.com/chiqiu23)

-   [Meaghan Brennan](https://github.com/teenyss)

-   [Emma Gardecki](https://github.com/emmagardecki)
