---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wetried

Names: Chi Qiu, Meaghan Brennan, and Emma Gardecki

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/wetried2)](https://CRAN.R-project.org/package=wetried2)

<!-- badges: end -->

The goal of wetried is to ...

## Installation

You can install the development version of wetried2 like so:

```{r}
devtools::install_github("chiqiu23/wetried")
```

## Load

```{r example}
library(wetried2)
## basic example code
```

## Available Tables

-   `smith_wbb_data`: dataset of Smith College women basketball games

```{r wbb_data}
library(readr)
smith_wbb_data <- read_csv("smith_wbb_data.csv")
head(smith_wbb_data)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
